%!TEX TS-program = xelatex
\documentclass[]{fancy-cv}
\hypersetup {
  colorlinks=true,
  urlcolor=bluepurple
}

\include{packages}
\include{header}
\include{info}
\include{interests}
\include{education}
\include{experience}
\include{programming}
\include{positions}

\newcommand\company{Atlassian}
\newcommand\position{\emph{Bitbucket Developer}}

\begin{document}
\header{\MakeLowercase\myfirstname}{\MakeLowercase\mylastname}{\MakeLowercase\mytitle}

\begin{aside}
  \section{contact}
    \href{mailto:\myemail}{\myemail}
    ~
    \myphone
    ~
    \myaddress%
    \mycity
  \section{website}
    \href{\mywebsite}{\mywebsite}
  \section{social}
    \href{http://facebook.com/\myfb}{fb://\myfb}
    \href{http://plug.google.com/\mygp}{google://\mygp}
    \href{http://www.linkedin.com/in/\mylinkedin}{linkedin://\mylinkedin}
  \section{code}
    \href{https://smf.io}{https://smf.io}
    \href{https://bitbucket.org/\myfb}{bitbucket://\myfb}
    \href{https://github.com/\myfb}{github://\myfb}
  \section{programming}
    \newforeach[expand list] \lang in \programming {%
      \lang
    }%
  \section{interests}
    \newforeach[expand list] \i in \interests {%
      \MakeLowercase\i
    }%
\end{aside}

\vspace{.8em}
\large
\today\\
\\
\\
Dear \company,

I'm applying for the open position of \position~which I found listed on your
site and through some friends on the Bitbucket team. I am seeking a full-time
position on the Bitbucket team and I believe my unique background in
computational mathematics and open-source projects about developer tools has
prepared me well for this position.
%
\newline\newline
%
My passion lies with building and improving tools for developers. That passion
helped led me to become a Mercurial developer. I have spent many years working
with Matt Mackall (project leader) on various contracts and have developed a
good relationship with most of the team. I have delved deep into the internals
of Mercurial: from in-memory merges to templating, from changeset evolution to
speeding up repository status. I have much experience with the mercurial
codebase. My most recent work with Mercurial adds the anticipated remote
branch feature.
%
\newline\newline
%
My Mercurial work helped foster a love for improving developer workflows. That
is why I contribute a lot of my free time to projects like
\href{https://kallithea-scm.org}{Kallithea}, an open-source, source code
manangement system that supports Mercurial as a backend. Modeled off the
successful Bitbucket, I would love the opportunity to use what I've learned
from Kallithea to help \company.
%
\newline\newline
%
I am eager to pursue this opportunity at \company. The best way to contact me
to set up an interview is by email. For further information about my commit
history, please visit my website. I look forward to hearing back from you.

\vspace{2em}
Sincerely,\\
\\
Sean Farley

\end{document}
