\documentclass[10pt]{article}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[colorlinks=true,hypertexnames=false,linkcolor=red,citecolor=blue]{hyperref}
\usepackage{currvita}
\usepackage{pdfsync}

% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
	\begin{list}{}{%
		\setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
		\setlength{\topsep}{0em}\setlength{\parskip}{0em}%
	}%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
	\begin{list}{\labelitemii}{%
		\setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
	}%
}%
{ \end{list} }

\pagestyle{empty}

\begin{document}

\newlength{\oldcvlabelwidth}
\newlength{\oldcvlabelsep}

\newcommand{\name}{Sean Farley}
\newcommand{\institute}{Louisiana State University}
\newcommand{\dept}{Department of Mathematics}

\begin{cv}{{\large \name}\\
{\normalsize Louisiana State University, 
Department of Mathematics\\
Email: {\mdseries \href{mailto:sean@math.lsu.edu}
	{sean@math.lsu.edu}} 
\hfill Phone: {\mdseries 209-SEANFAR} \hfill 
Web: {\mdseries \href{http://www.seanfarley.org/}
	{www.seanfarley.org}}}
}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\oldcvlabelsep}{\cvlabelsep}

\setlength{\cvlabelwidth}{1em}

\begin{cvlist}{Education}
	\item \emph{Ph.D.}, in-progress\\
	\institute, GPA: 3.67/4.0
	\item \emph{M.S., Mathematics}, May 2008\\ 
	\institute, GPA: 3.62/4.0
	\item \emph{B.S., Mathematics; minors in Physics and Chinese}, May 2006\\
	\institute, GPA: 3.25/4.0
\end{cvlist}

\setlength{\cvlabelwidth}{0em}
\setlength{\cvlabelsep}{\labelsep}
\begin{cvlist}{Technical Experience}
\item
	\begin{itemize}\itemsep=0.25em
	\item Graduate assistantship focused on assisting B.~Bourin in graduate courses
		with writing support code in C/C++ and tutorial lectures. Also included
		installation, configuration and administration of LDAP, http and svn
		servers for a cluster. General departmental computer support: design of a
		Kerberos-based authentication system.
	\item Worked with H.~Zhang and L.~Curfman under a Givens Fellowship to add
		PETSc time-stepping and preconditioners to a edge plasma simulation code from LLNL.
	\item Undergraduate research included implementing parallel programming using MPI and PETSc;
		structuring data, scatter and gather among processors; as well as working with a general
		relativity research group that used OpenGL and CAVE implemented with C++ libraries to
		utilize virtual reality aspects of the SGI ImmersaDesk on modeling binary stars.
	\item Various undergraduate jobs included working with small teams to solve numerous business
		and technical problems. Use of design patterns, databases, threads, security, web services in .NET,
		and xml were highly used; designing online web applications with extensive database access using PHP,
		creating graphics for web pages.
	\end{itemize}
\end{cvlist}

\begin{cvlist}{Technical Skills}
\item
\begin{itemize}\itemsep=0.25em
	\item Over 5 years experience with building, maintaining, and programming on computing clusters
	\item Over 10 years experience in open source projects such as Apache Web Server, MySQL, PHP, OS Kernels, etc.
	\item 15 years programming experience with C/C++, Java, Visual Basic, Perl, PHP, JavaScript,
		HTML, and SQL including much experience with Visual C++, C\#, and .NET Applications
	\item Compiled, setup, and maintained DHCP, DNS, LDAP, Kerberos, Database and Email servers on
		FreeBSD and other *nix operating systems
	\item Extensive academic and work experience in computer related domains: design patterns,
		software design, web development, networking, etc.
\end{itemize}
\end{cvlist}

\begin{cvlist}{Extracurricular}
\item
\begin{itemize}\itemsep=0.25em
	\item Math Club - President 2005-2006
	\item Boy Scouts of America - Eagle Scout (4 palms)
\end{itemize}
\end{cvlist}

\end{cv}
\end{document}

