\documentclass[10pt]{article}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[resetlabels]{multibib}
\usepackage[ManyBibs]{currvita}
\usepackage{pdfsync}

% Initialize each paper type for which you need a bibliography.
% Just a dummy parameter is necessary.
\newcites{refpaper}{foo}
\newcites{unrefpaper}{foo}
\newcites{journal}{foo}
\newcites{techreport}{foo}
\newcites{submitpaper}{foo}
\newcites{classproject}{foo}

% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
	\begin{list}{}{%
		\setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
		\setlength{\topsep}{0em}\setlength{\parskip}{0em}%
	}%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
	\begin{list}{\labelitemii}{%
		\setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
	}%
}%
{ \end{list} }

\newcommand{\TikZ}{Ti\emph{k}Z}

\begin{document}

% Specify the bibtex style that you want for each paper type
\bibliographystyle{unsrt}
\bibliographystylerefpaper{unsrt}
\bibliographystyleunrefpaper{unsrt}
\bibliographystylesubmitpaper{unsrt}
\bibliographystylejournal{unsrt}
\bibliographystyletechreport{unsrt}
\bibliographystyleclassproject{ieeetr}

% We'll use this length to change the defaults in some of our lists.
\newlength{\oldcvlabelwidth}
\renewcommand*{\cvbibname}{}
\newcommand{\name}{Sean Farley}
\newcommand{\institute}{Louisiana State University}
\newcommand{\dept}{Department of Mathematics}

% This is what will appear at the very top of your CV.
\begin{cv}{\name\\{\large \itshape Curriculum Vitae}}

% Items have more vertical space between them than line breaks.
% Note: if you want a linebreak after each cvlist title, you can do:
% \begin{cvlist}{Title \hspace{3in}}
\begin{cvlist}{Contact}
	\item
	375 Lockett Hall\\
	\institute\\
	Baton Rouge, LA 70803-4918
	\item Phone: 209-SEANFAR
	\item sean@math.lsu.edu
	% The tilde doesn't show up well in LaTeX, the \sim symbol looks
	% much better.  Though, you can't copy and paste it from your PDF
	% like you can with a tilde.
	\item http://seanfarley.org
\end{cvlist}

\begin{cvlist}{Research Interests}
	\item Finite element methods, numerical linear algebra, software collaboration using design patterns, implementing preconditioners / solvers
		% 
		% Network security (both Internet and wireless), 
		% protocol design for wireless devices,
		% wireless applications, peer-to-peer networks.
\end{cvlist}

\begin{cvlist}{Education}
	\item \emph{Ph.D., Mathematics}, in progress\\
	\institute\\
	Baton Rouge, LA
	% Sublists don't have any extra vertial space.
	\begin{sublist}
		% \item Thesis: \textit{}
		\item Adviser: Prof. Robert Lipton
		\item Committee: Prof. Susanne Brenner, Prof. Li-yeng Sung, Prof. Bill Hoffman, and Prof. Hongchao Zhang
		\item GPA: 3.67/4.0
	\end{sublist}
	\item \emph{M.S., Mathematics}, May 2008\\ 
	\institute\\
	Baton Rouge, LA
	\begin{sublist}
		% \item Thesis: \textit{}
		% \item Adviser: Prof.
		\item GPA: 3.62/4.0
	\end{sublist}
	\item \emph{B.S., Mathematics}, May 2006\\
	\institute\\
	Baton Rouge, LA
	\begin{sublist}
		\item GPA: 3.25/4.0
		\item Minors: \emph{Physics} and \emph{Chinese}
	\end{sublist}
\end{cvlist}

% \begin{cvlist}{Honors}
% \item
% 	\emph{US National Science Foundation Fellowship}
% 	\begin{sublist}
% 	\item Awarded in 2009
% 	% \item Acceptance Percentage: 16.2\% (903/5560)
% 	\end{sublist}
% \item
% 	\emph{Givens Fellowship}
% 	\begin{sublist}
% 	\item Awarded in 2008
% 	% \item Acceptance Percentage: 21.3\% (285/1339)
% 	\end{sublist}
% \end{cvlist}

% After you have finished your CV, you may need to manually insert
% some pagebreaks to make it look nice.
\pagebreak

% cvlist items can take dates as a parameter.
\begin{cvlist}{Employment}
	\item[Summer 2009] Student Co-op\\
	Argonne National Laboratory, MCS\\
	Chicago, IL\\
	\\	
	Continued work with H.~Zhang and L.~Curfman to build extendable code in collaboration
	with LLNL physicists by adding robust PETSc solvers to BOUT++, a parallel edge turbulence
	framework for plasma fusion simulation. This code has been successfully integrated
	into BOUT++ and has been released in version 0.7.	 
	
	\item[8/2006--Present] Graduate Assistant\\
	\institute, \dept\\
	Baton Rouge, LA\\
	\\
	Assisted B.~Bourdin in a graduate class on elliptic solvers and wrote 
	supporting code in C/C++ using PETSc. Installation, configuration and 
	administration of LDAP, http and svn servers for a cluster. General 
	departmental computer support: design of a Kerberos-based authentication system.
	
	\item[Summer 2008] Givens Internship\\
	Argonne National Laboratory, MCS\\
	Chicago, IL\\
	\\
	Worked under H.~Zhang and L.~Curfman to add PETSc time-stepping and 
	preconditioners to a edge plasma simulation code from LLNL.
	
	\item[Summer 2006] Research Programmer with B.~Bourdin\\
	\institute, \dept\\
	Baton Rouge, LA\\
	\\
	Parallel programming using MPI and PETSc; structuring data, scatter and gather among processors.
	
	\item[6/2003--8/2006] Programmer\\
	Velocity Squared, LLC\\
	Baton Rouge, LA\\
	\\
	Worked with small teams to solve numerous business and technical problems. Used design
	patterns, databases, threads, security, web services, and xml.
	
	\item[8/2001--7/2002] Student Programmer\\
	Louisiana Department of Education\\
	Baton Rouge, LA\\
	\\
	Designing online web applications with extensive database access using PHP and 
	creating graphics for web pages. Configuring hardware, installing software, 
	and teaching workshops on Javascript, SQL, and Adobe Photoshop 6.
	
	\item[8/2001--5/2002] Virtual Reality / 3D Programmer with J.~Tohline\\
	\institute, \dept\\
	Baton Rouge, LA\\
	\\
	Worked with a general relativity research group that used OpenGL and
	CAVE implemented with C++ libraries to utilize virtual reality aspects of
	the SGI ImmersaDesk on modeling binary stars.
	
	\item[8/2000--5/2001] Database / Dynamic Web Programmer\\
	LA School for Math, Science, and the Arts\\
	Natchitoches, LA\\
	\\
	Designing and implementing web-based programs for students and faculty,
	utilizing server side languages such as PHP, Java Server Pages, and Perl.
	Also wrote a complete online application for registering students for classes and seminars.
	
	\item[8/1999--5/2000] Web Programmer\\
	LA School for Math, Science, and the Arts\\
	Natchitoches, LA\\
	\\
	Creating web pages using HTML, CSS, and JavaScript for faculty, including
	graphic design and knowledge of web server maintenance.
\end{cvlist}

% These commands will make our papers be indented after the first line
% to make the author's name stand out more.  Also, we reduce the
% indentation of the paper type titles (e.g., Journal Papers,
% Conference Paper) compared to regular cvlist items.
\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\renewcommand*{\bibindent}{1.5em}
% Do bibaddtoleftmargin instead of biblabelsep if you're
% not using manybib or open bib
%\renewcommand*{\bibaddtoleftmargin}{1.5em}
\newcommand*{\biblabelsep}{1.5em}

% To update, before doing latexmk, run:
% bibtex journal
% bibtex refpaper
% bibtex unrefpaper
% bibtex techreport
% \begin{cvlist}{Publications}
% 	% With multibib, each cite command has the type after it.
% 	\item \textbf{Journal Papers}
% 	\nocitejournal{miller04mac_vitae}
% 	\bibliographyjournal{vitae}
% 	\item \textbf{Conference Papers} 
% 	\nociterefpaper{miller06leveraging_vitae}
% 	\nociterefpaper{miller05improving_vitae}
% 	\nociterefpaper{miller05exploring_vitae}
% 	\nociterefpaper{miller04power_vitae}
% 	\nociterefpaper{miller04minimizing_vitae}
% 	\bibliographyrefpaper{vitae}
% 	\item \textbf{Submitted Papers} 
% 	\nocitesubmitpaper{sengul05exploring_vitae}
% 	\nocitesubmitpaper{miller05using_vitae}
% 	\bibliographysubmitpaper{vitae}
% 	\item \textbf{Technical Reports} 
% 	\nocitetechreport{miller05errata_vitae}
% 	\nocitetechreport{miller04ondemand_vitae}
% 	\nocitetechreport{miller03hybrid_vitae}
% 	\bibliographytechreport{vitae}
% \end{cvlist}
% Reset the label indentation
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Research Experience}
	\item \textbf{Graduate Coursework}
	\begin{sublist}
		% \item 
		% My work focuses on \textit{security} and \textit{energy efficiency}
		% in wireless
		% multihop networks, particularly sensor networks.  In the
		% security domain, I proposed a key distribution protocol to
		% provide symmetric, pairwise keys that, with high
		% probability, are unknown to eavesdroppers.  This was the first
		% work to use the underlying wireless channel diversity
		% to address this problem.  In the energy efficiency domain, most
		% power save protocols use static sleeping and listening intervals
		% regardless of the network environment.  My work looks at
		% adaptively adjusting these intervals in response to
		% network traffic.  Additionally, I have proposed methods of using
		% carrier sensing to further improve the energy efficiency of
		% power save protocols and a lightweight protocol to address the
		% energy-latency tradeoff for broadcast dissemination in sensor
		% networks.
		
		\item Fluid Dynamics and Computational Methods, Dept. of Computer Science, LSU.
		\item Ordinary Differential Equations, Dept. of Mathematics, LSU.
		\item Finite Element Method: Analysis and Implementation, Dept. of Mathematics, LSU.
		\item Elliptic Solvers: Advanced parallel implementation \& related topics, Dept. of Mathematics, LSU.
		\item Fast Solvers, Dept. of Mathematics, LSU.
		\item Numerical Linear Algebra, Dept. of Mathematics, LSU.
		\item Applications of spectral theory material science, Dept. of Mathematics, LSU.
		\item Elliptic PDEs on non-smooth domains, Dept. of Mathematics, LSU.
		\item Finite Difference Methods, Dept. of Mathematics, LSU.
		\item Free discontinuity problems in image processing \& fracture mechanics, Dept. of Mathematics, LSU.
	\end{sublist}

	% \item \textbf{Graduate Class Projects}
	% This sublist looks better with bullets.
	% \begin{subbulletlist}
		% \item Chance to expand specific projects I've done with Brenner and Bourdin\\
		% \item \textit{Improving Fault Tolerance in AODV}\\
		% Joint work with Jungmin So in Fall 2002.  Designed, simulated,
		% and evaluated (using \textit{ns-2})
		% techniques to maintain multiple routes in an ad-hoc routing protocol.
		% \item \textit{Improving Connectivity in a Scatternet Formation
		% Algorithm}\\
		% Joint work with Cristina L. Abad in Spring 2002.  Designed,
		% simulated, and evaluated (using a custom built simulator written
		% in C) a protocol to provide greater
		% connectivity in Bluetooth scatternet formation. 
		% \item \textit{Log Correlation for Intrusion Detection}\\
		% Group project in Spring 2003.  Investigated how information 
		% from various system
		% logs can be used to identify specific attacks.  Subsequent work 
		% by some group members led to a publication based on the
		% project:  
		% \renewcommand*{\biblabelsep}{1.5em}
		% \nociteclassproject{abad03log}
		% \bibliographyclassproject{vitae}
		% \item \textit{Tools for Middle School Students to Create Vignettes}\\
		% Joint work with Jeffrey Naisbitt and Naomi Caldwell in Spring
		% 2003.  Designed, implemented, and did user-testing on a
		% tool (using Java Swing) to allow students to create life 
		% stories using an instant messenger-like interface.
	% \end{subbulletlist}
	\item \textbf{Awards}
	\begin{subbulletlist}
		\item NSF Fellowship under B.~Bourdin
		\item Givens Fellowship under L.~Curfman
		\item First place in Mathematics Association of America contest - 2003, 2005
		\item First place in LSU sponsored computer programming competition
		\item Graduated high school with distinction in computer science (A JSP/ODBC Client/Server Registration Package)
		\item Louisiana School Excellence Awards in Computer Science, Physics, and Mathematics
		% \item DARPA/NSF Student Travel Grant (US \$400--750) for IEEE MASS 2005
	\end{subbulletlist}
	% \item \textbf{Undergraduate Work}
	% \begin{subbulletlist}
	% 	\item Participated in the NSF-funded Summer Undergraduate 
	% 	Research Experience (SURE) at Clemson University in 1999.
	% 	\item Worked in Parallel Architecture Research Lab (PARL) 
	% 	at Clemson University for two years.
	% 	\item Projects included designing user interfaces (using Java Swing)
	% 	for scientific
	% 	computing problem solving environments to allow message passing
	% 	between modules and array partitioning.
	% \end{subbulletlist}
	% \item \textbf{External Reviewer}
	% \begin{sublist}
	% 	\item \textit{IEEE Transactions on Mobile Computing}, 
	% 	\textit{IEEE Transactions on Wireless Communications}, 
	% 	\textit{IEEE Transactions on Information Forensics and
	% 	Security}, \textit{IEEE Communications Magazine}, 
	% 	MobiQuitous 2004, IEEE WCNC 2004, IEEE ICC 2005, and MASS 2006  
	% \end{sublist}
	
	\item \textbf{Talks and Seminars}
	\begin{subbulletlist}
		\item ``An Introduction to \TikZ: Integrating Graphics within \LaTeX,'' SIAM Student Seminar, Oct. 30, 2009
		\item ``\texttt{BOUT++} Status and Suggestions: A Look at Building Extendable Code,'' LLNL Physical and Life Sciences, Aug. 17th, 2009
		\item ``Parallel Programming: An Introduction to PETSc and Distributed Arrays,'' LSU  Math Seminar, Oct. 30, 2009
		\item ``Basic Parallel Programming: An Introduction to Linux and MPI,'' LSU Math Seminar, Oct. 14, 2009
		\item ``C Introduction: Pointers and Memory Allocation,'' LSU Math Seminar, Oct. 1, 2008
	\end{subbulletlist}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\begin{cvlist}{Memberships}
	\item[2007--present] Student Officer, Society for Industrial and Applied Mathematics (SIAM)
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Technical Skills}
	% \item \textbf{Proficient}
	% \begin{sublist}
	% 	\item C/C++, Java, LaTeX, Matlab, PETSc, MPI
	% \end{sublist}
	% \item \textbf{Familiar} 
	% \begin{sublist}
	% 	\item PHP, Perl, Ruby, Python
	% \end{sublist}
	
	% \begin{itemize}\itemsep=0.25em
		\item Over 5 years experience with building, maintaining, and programming on computing clusters
		\item Over 10 years experience in open source projects such as Apache Web Server, MySQL, PHP, BSD and Linux Kernels.
		\item 15 years programming experience with C/C++, Java, Visual Basic, Perl, PHP, JavaScript,
			HTML, and SQL including much experience with Visual C++, C\#, and .NET Applications
		\item Compiled, setup, and maintained DHCP, DNS, LDAP, Kerberos, Database and Email servers on
			FreeBSD and other *nix operating systems
		\item Extensive academic and work experience in computer related domains: design patterns,
			software design, web development, networking, etc.
	% \end{itemize}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\begin{cvlist}{Extracurricular}
	\item[2007--2009] SIAM Webmaster
	\begin{subbulletlist}
		\item Responsible for setting up web server
		\item Maintained Wordpress
		\item Wrote custom scripts to maintain membership and calendar
	\end{subbulletlist}
	\item[2005--2006] Math Club - President
	\item[1994--1999] Boy Scouts of America - Eagle Scout (4 palms)
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Miscellaneous}
\item \textit{Citizenship:} United States of America
\item \textit{Marital Status:} Unmarried
\end{cvlist}

\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\end{cv}
\end{document}

